An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-10-04 nips_2016.tex
updates

\author{
  Haoyu Chen, Daniel Seita, Xinlei Pan, John Canny \\
  University of California, Berkeley \\
  \texttt{\{haoyuchen,seita,xinleipan,canny\}@berkeley.edu}
 }

>>>>

\author{
  Haoyu Chen\textsuperscript{*}, Daniel Seita\textsuperscript{*},
  Xinlei Pan\textsuperscript{*}, John Canny\textsuperscript{*}$^{\dag}$ \\
  * University of California, Berkeley \\
$\dag$ Google Research, Mountain View, CA\\
  \texttt{\{haoyuchen,seita,xinleipan,canny\}@berkeley.edu}
 }
